### 2019-08-01 thesis.tex
not sure

Since the ubiquity of plasmas in space came as a fact, astrophysicists and
plasma physicists have been noticing an increasing necessity for exchanging
knowledge and mutually collaborating with their results. In this arrangement,
plasma physics provides theoretical, computational, and laboratory models
that might help with the interpretation and propose a physical explanation
for astrophysical observations. Astrophysics, on the other hand, contributes
with data from observations of phenomena that are unique to cosmic plasma and
might be used to confirm theoretical and computational predictions on plasma
physics, and also to compare with experimental results\cite{tsypa,Kulsrud2005}.
A particular field of research that has been acting for a long time as a bridge
between these two areas is the solar physics.

>>>>

Since the ubiquity of plasmas in space came as a fact, astrophysicists and
plasma physicists have been noticing an increasing necessity for exchanging
knowledge and mutually collaborating with their results. A particular field
of research that has been acting for a long time as a bridge between these two
areas is the solar physics. The accessibility of the solar plasma to direct,
in situ measurements, highly resolved remote sensing and high-resolution
spectroscopy turned the solar system into Earth's space physics laboratory.

A recent example of this complementarity is
presented in Ref. \cite{Peterson2019}, where the authors reproduced in the
laboratory a magnetic structure called, \emph{Parker spiral}, which is
related to the acceleration process of solar -and stellar- winds. The
authors also compare their results with numerical simulation of the same
structure. Astrophysics, on the other hand, contributes with data from
observations of space plasma phenomena that might be useful for testing
theoretical predictions, and comparing with numerical and experimental
results. In Ref. \cite{Chen2019}, for instance,
